---
title: "p8105_hw1_yx2710"
output: github_document
---

```{r setup}
library(tidyverse)
```


Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```

```{r}
names(penguins)
nrow(penguins)
ncol(penguins)
mean(pull(penguins,flipper_length_mm), na.rm = TRUE)
```

The penguis dataset has `r ncol(penguins)` columns and `r nrow(penguins)` rows, The names of the 8 variables are `r names(penguins)`. The mean flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`mm.


```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

```{r}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

Problem2

```{r}
p2_df = tibble(
  num_vec = rnorm(10),
  logi_vec = num_vec > 0,
  char_vec = c("data", "science","is","very","interesting","and","useful","as","well","yeah"),
  fac_vec = factor(c("alpha","beta","omega","alpha","beta","beta","beta","omega","beta","beta"))
)
```

```{r}
mean(pull(p2_df, num_vec))
mean(pull(p2_df,logi_vec))
mean(pull(p2_df,char_vec))
mean(pull(p2_df,fac_vec))
```
I tried to get the mean of each variables, and I can take the mean of numeric vector and logical but not the charactor vector and the factor vector and I only  got "returning NA"


```{r}
as.numeric(pull(p2_df,logi_vec))
as.numeric(pull(p2_df,char_vec))
as.numeric(pull(p2_df,fac_vec))
```

When I tried to convert the type of variables, I succeeded to convert logical veoctor and fanctor vector to numeric vector and got their means, however, the character vector still showed NA. We cannot take the mean of character vector.

